\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity}

### 2013-12-03 docs/paper/paper.tex
Added section on extensions of PC.

\paragraph{Conservative PC}
In a more recent publication by Ramsey et al. \cite{ramsey2012} a weaker but still sufficient assumption for graph faithfulness in PC algorithm is introduced.
Through this weaker but still adjacency-faithful assumption, the method is more cautious than PC algorithm in drawing unambiguous conclusions on causal orientations.
That is why this method is named Conservative PC (CPC).
The resulting algorithmic changes provide better results and is able to mark unshielded triples as unfaithful.
However, CPC requires a significant amount of additional conditional independence tests.

\paragraph{...}

>>>>

% Conservative PC
\paragraph{Conservative PC}
Step x in PC algorithm assigns shielded triples based on a single separating set. % TODO: Add step
Simply put, it is assumed the single found separating set is enough to show conditional independence. 
Ramsey et al. \cite{ramsey2012} introduce a weaker but still sufficient assumption for directing unshielded triples.
Through this weaker but still adjacency-faithful assumption, the method is more cautious than PC algorithm in drawing unambiguous conclusions on causal orientations.
That is why this method is named Conservative PC (CPC).
The resulting algorithmic changes provide better results and is able to mark incorrectly unshielded triples as unfaithful.
Sadly, CPC requires a significant amount of additional conditional independence tests, exponential in the largest branching degree of the tested structure.

% Multiple sepsets
\paragraph{Multiple Separating Sets}
The idea of CPC, to make a weaker assumption on graph faithfulness, is very potential.
Instead of doing additional tests, one could attempt to determine causal unfaithfulness with less dependency tests.
An adaptation to PC algorithm that would not increase the order of complexity is once a separating set is found, to test all other vertex subsets of the same order as well.
This finds all separating sets of the lowest order without increasing complexity.
Orienting an unshielded triple $\left<A,B,C\right>$ requires $B$ not to occur in any separating set of $(A,C)$.
By having more than one separating set, this constraint is strengthened.

% Unfaithfulness test
One could use these additional separating sets to test oriented unshielded triples for unfaithfulness, similar to CPC.
Apart from serving as a sanity check, this could serve as the basis of a repair algorithm for errors made by PC.

% Explicit test
A more direct way to decrease faulty orientation of an unshielded triple $\left<A,B,C\right>$ is to check whether adding $B$ to a separating set of $(A,C)$ makes the pair conditionally dependent.
If so, the graph is likely to be more faithful to its modeled distribution.

\paragraph{EMS PC}
...
